\documentclass[10pt]{article}
\setlength{\parindent}{0pt}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[left=1.0cm,top=1.2cm,right=1.0cm,bottom=1.2cm]{geometry} % Compact margins with breathing room
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

% Link colors
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

% Section Formatting - Tightened spacing
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

\begin{document}

% HEADER
\begin{center}
    {\Huge \textbf{CUONG DAO}} \\ \vspace{6pt}
    Ho Chi Minh City, Vietnam \\
    (+84) 902 030 918 \\
    \href{mailto:dqcuong93@gmail.com}{Gmail} \textbullet \ \href{https://www.linkedin.com/in/cuongdao93}{LinkedIn} \textbullet \ \href{https://github.com/dqcuong93}{Github} \\
\end{center}

\vspace{-2pt}

% EXPERIENCE
\section{Professional Experience}

\textbf{Freelance - Independent Projects} \hfill Remote \\
\textit{Technical Lead / Senior Backend Engineer} \hfill Mar 2021 - Present
\begin{itemize}[itemsep=1pt, topsep=2pt]
    \item Architected end-to-end backend infrastructure for \textbf{6+} independent platforms across FinTech, EdTech, and digitization, managing system design through production deployment.
    \item Scaled the Meta Wisdom backend to serve \textbf{1,000+ concurrent} users at \textbf{380ms median latency} with zero failures, optimizing performance via Redis caching and Gunicorn tuning.
    \item Led the TradeModules infrastructure migration from Kubernetes to a leaner Docker-based deployment, delivering a production-grade, white-label trading platform for a licensed Vietnamese securities brokerage, maintaining zero reported incidents since go-live, and achieving \textbf{Top 50 at Startup Wheel}.
    \item Engineered the DigiSER master-slave architecture using Django and Vue 3, integrating offline OCR and bulk digital-signing tools to process\textbf{ 40,000-100,000+} files per batch.
\end{itemize}

\vspace{6pt}

\textbf{VietNam Cloud Services - V!Studios} \hfill Vietnam \\
\textit{Senior Backend Developer} \hfill Jul 2020 - Present
\begin{itemize}[itemsep=1pt, topsep=2pt]
    \item Built and maintained scalable backend services for 3 production-grade cloud platforms spanning document automation and luxury travel.
    \item Developed the Quiqtext serverless OCR pipeline leveraging AWS Textract and Lambda, successfully reducing document processing time by \textbf{80\%}.
    \item Modernized the legacy Trade To Travel monolithic system to a decoupled Docker and Wagtail architecture, delivering seamless backend modernization with zero production downtime.
    \item Enforced code quality and reliable releases via CI/CD pipelines, Pytest, and Agile delivery, maintaining \textbf{>60\%} test coverage.
\end{itemize}

\vspace{6pt}

\textbf{PTSC - PetroVietnam Technical Services Corporation} \hfill Vietnam \\
\textit{IT Specialist} \hfill Oct 2015 - Jul 2020
\begin{itemize}[itemsep=1pt, topsep=2pt]
    \item Architected an enterprise asset management system to replace manual tagging and paper-based tracking, assigning unique system IDs to computers, furniture, and equipment, and integrating endpoint monitoring to track real-time asset location and flag unauthorized software.
    \item Digitized manual, paper-based approval workflows (leave requests, supply requisitions) into an online system with multi-level electronic sign-off, eliminating sequential physical paperwork and accelerating cross-departmental approval cycles.
\end{itemize}

% SKILLS
\section{Technical Skills}
\begin{itemize}[itemsep=1pt, topsep=2pt, leftmargin=*]
    \item \textbf{Languages:} Python, Bash, JavaScript.
    \item \textbf{Backend \& Frameworks:} FastAPI, Django, Wagtail, Serverless Framework, Vue 3, Inertia.js.
    \item \textbf{Databases:} PostgreSQL, TimescaleDB, MongoDB, Redis.
    \item \textbf{Cloud \& DevOps:} AWS (EC2, S3, Lambda, Textract), Docker, Kubernetes, CI/CD Pipelines, Bitbucket Pipelines.
    \item \textbf{Methodologies:} Agile, DevOps, TDD.
\end{itemize}

% EDUCATION
\section{Education}
\textbf{Western Sydney University} \hfill Australia \\
MBA, Information \& Communications Technology \hfill 2018 - 2020

\vspace{4pt}

\textbf{Saigon Technology University} \hfill Vietnam \\
Engineer, Computer Science \hfill 2011 - 2015

\end{document}